\chapter{Seroquel}
My family goes to Connecticut for Christmas, where my grandparents live.  My
mother and my grandmother (a middle school pincipal) made the decision that I
would visit a special psychologist in Connecticut.

I could feel that I was making my family miserable at my grandparent's house.
At home in Buffalo, I felt okay with my situation being on leave of absence.
After an initial reluctance to give up on the semester, I felt an intense sense
of relief once I realized I wasn't going back to school.  I lay in my bed with my
phone, listening to classical music.  It was truly winter, after Thanksgiving,
and I had a wired heating pad.  During Christmas I wanted to continue this
lifestyle.  I had made a list of 100 books I wanted to read in the new year,
and I wanted to spend eight hours a day reading.  I had my bookstand and a copy
of Harold Bloom's ``The Western Canon'', and I tried to set it up in the dining
room away from everyone.  My mom came in and told me sternly that this wasn't
okay.  I argued.  This happend for days.  I was making my family miserable.  The
thought of playing with my toddler cousins or other high-spirited activities was
painful.  My mother and even father accused me of being unempathetic and
selfish.  Very soon I was miserable as well.

We went to visit the psychologist on a workday between Christmas and New
Years.  She worked out of her own home. 

My parents went in and talked to her for at least an hour.  I had my notebook
with me, and drew the door to her office.   ...

When I returned to Buffalo, I began to row 5 kilometers most days.  The first
time I tried to row five kilometers, I stopped at about three kilometers in, but
then started up again and finished.  I wrote the total time in my Moleskeine
planner.  I also used the Moleskeine to write down the PHP/JavaScript/HTML
tutorials I completed and the books I planned to read.  This was basically how I
passed the winter of 2010-2011.  I had to withdraw from the literature classes I
took at 

My host mother in Taiwan had given me the planner;     It had inpsired me to try
to keep a daily planner.  WHen I started using it, right before the beginning of
2010, I had imagine the decade of the '10s as ``my decade''.  It was the decade
I would have to be successful in, or else.  I'd be 28 at the end of the decade.
1/10th of that decade was now almost done.

Bookstore job.  

\chapter{Learning to Program}
Hipster Runoff personals.

\chapter{Robert Horning}

After landing, I got my bag and waited for Marie to arrive.  I finally found her
waiting outside.  When she saw me she made an inarticulate noise and hugged my
chest.

``Hi,'' I said.

I shivered from being on the plane.  We waited in a long line for a taxi to
Manhattan.  We were mostly silent, but it was not awkward. 

The movement and wind of the taxi made things feel less ominous.  I put my arm
around her and and enjoyed looking out the window at the orange, complicated
night outside.  It was my first time in New York without my parents.  In the
tunnel under the river, Marie kissed me.  It was not a great kiss, but it put
to rest the mild anxiety that things weren't going well.

When we got to the hotel I paid the \$50 for the cab, and we made our way to the
room.  It was a little more dingy than I had expected.  I could tell that we
both liked it, though.

We had planned to drink 2.5 beers before we had sex.  As we sat on the bed,
talking about the guy she had met on her flight, I felt more and more
comfortable with her voice.  The light of the room was very warm and home-like.
When room service came with our beer and food Marie smiled at me as I fumbled with the
tip.  

I drank one of the Budweisers quickly and watched Marie eat steak and eggs.  

"Do you want to have sex now?" Marie asked, placidly.

"Yes," I said, smiling.

"Let's take a shower first."

Marie went into the very small bathroom and took off her wrinkled button
down and shorts.  She dropped them on the floor, where they became damp with the
water from the tub.  I took off my clothes, shivering again.  We sat
facing each other in a few inches of warm water.

I touched her shoulders, which had been scarred by acne.  She ran her fingers
over the hair on my upper thighs.

"I want to give you a blowjob," she said.

"Alright."

"Could you, like, kneel?"

It was my first time getting a blow job, and I was surprised by the feel of
teeth and stray hair.  The fact that we were in a tub was somewhat funny, to me.

"You have really big balls," she said, when she stopped.

We got out of the tub and went to the bed.  I felt more confident.  We kissed
and then had sex.  As we had discussed before, I didn't use a condom.  I came
pretty quickly and Marie checked that I hadn't come inside of her.  

"Don't worry," I said. 

After a period of quiet conversation, Marie asked me to get her a pack of
cigarettes.  I was happy to take a walk alone, to process things in cool night
air.

I saw a smoke shop but walked past it, drawn towards Times Square.  It was late
enough that Times Square was relatively quiet, but still incredibly bright.  I
memorized the shapes of the black and reflecting buildings above me, most
seemingly from the late 80s and reminiscent of late 80s neoliberalism.  I felt
that I had lost my virginity the right way, for me.  

Herb's last day

  
\chapter{Mainland China}

\input{chapters/china.tex}

\chapter{The University at Buffalo}
While I was very involved with the Internet in the spring of 2012, I also
started to have more a ``real life''.  I saw a flyer advertising the men's
rowing team, looking for people over six feet tall.   I wanted to
meet people and go to parties at UB. 

I went to the information session advertised on the poster.  I was impressed by
 broad chest of one of the rowers at the session.  I decided I
wanted to look like that.  I put my name down.

In the spring of 2012, I was taking programming, accounting, economics, and
math classes.  I cried bitterly after my first accounting test.  All of my
other classes were very easy and I got near-perfect grades.

In February I showed up to a few land workouts, where we ran stadiums or did
some erging.  I think I missed about half the practices, just as I missed about
half of the cross country, track, or wrestling practices in high school.
Something changed, though, in the beginning of March.

I drove myself to the boathouse (more of a quonset hut) early in the
morning.  I was late, so they didn't put me in a boat, but told me to go for a
run.  I had been up too late on the Internet most nights the past week.  I ran
behind one of the other rowers, barely keeping up.  I described the pain to
myself in words: I felt my shoulder muscles heat up and become loose, my chest
become a golden cage, a golden twinging cage.  Sweat dried onto my face and
burned the corners of my eyes.  When we finished, I felt good.  I told the coach
that I could go on the training trip during spring break.  

Then I got in my car and wrote a tumblr entry describing how I wanted to go to
Sports College: I needed a coach to tell me when to eat, when to sleep, when to
work.  I needed to learn to control my fatigue and pain.  I could take care of
my own mind, I thought.


\chapter{Writing Advice}

 One weekend in February, I flew to New York to go to a reading by Marie
Calloway, Tao Lin, Spencer Madsen, and Megan Boyle.  It was my first time in
New York since I'd flown there to meet Marie when we were Internet boyfriend
and girlfriend.  

After arriving, I took the subway to Wall Street.  I was interested in Finance
as a career and Occupy Wall Street.  Zucotti Park was desolate, surrounded by
portable police watchtowers. A handful of people were protesting, or just there.
I admired a statue of a banker eating his lunch, staring into his slim
briefcase.

I wandered away from Wall Street, trying to find somewhere to charge my
Blackberry  so that I could keep trying to get in contact with Marie. I was
worried that I would be isolated and alone for the whole long weekend.  I was
becoming slightly more confident, and I didn't want to damage this confidence by
feeling ugly, disillusioned, and left out at the reading.

I spent the rest of the long, dark afternoon and evening wandering around
Williamsburg.  My duffle bag was chafing my legs.  Eventually I sort of gave up
on Marie messaging me back, and got a hotel room at the Brooklyn Sheraton.  I
felt calmed, and took a picture of the hotel room and put it on facebook.  I
wrote an email to the Yale cofounders of a location-based chat service that I
thought was interesting, and felt thrilled and excited when I recieved a
response back: yes, they'd be happy to set up a call.  With Marie off my mind, I
got ready for bed.  

I checked facebook one last time.  There were a bunch of messages from Marie.
She was upset and drunk and wondering where I was.  I felt excited, relieved: I
messaged her that'd I'd come to her if she gave me an address, and went down to
the hotel lobby to get a cab.  It was almost midnight.

The cab stopped at the address, around Union Square.  Marie was supposed to meet
me outside.  I got out of the car and saw her.  For a moment, it was like she
was pretending not to see me, or expecting me to come to her.  She was wearing
very short shorts and looked unstable.  I waved her towards the cab.  

She got in and put her head on my shoulder.

``Thank God that was so awful, I needed to get away,'' she said.  I felt sort of
validated: I didn't really trust the Internet women friends she was staying
with.  I told the cab driver to take us to the address of the first bar I found
on yelp in Brooklyn, and wondered how he interpreted Marie and I: did he think
she was a sex worker?  

Marie started crying, and I smoothed her hair.  She cried until we got to
Brooklyn.

We went into an empty bar, and Marie was suddenly more cheerful.  She talked
about the people she had met at the readings, and told me that I was special.
After a couple of sweet whiskey drinks we left the bar, and went to find 
food.  While crossing the street, Marie asked me ``Are we going to have sex,
Patrick?'' and I said ``I don't know...probably?''

Marie got chicken wings or something and we got a cab back to the Sheraton.  The
driver couldn't find it and I felt calm and detached, trying to give directions.  

When we got back to the hotel, Marie took a shower, and got onto the bed in the
doggy style position.  ``Fuck me,'' she said.  I took off my khakis, button
down, and sweater, and kneeled on the bed with a condom.  I felt ambiguously
turned on due to the alcohol and comfort of the hotel room, and put the condom
on.  When I saw the hair of her vagina and touched my body to her slightly wet
skin, trying to push my way into her, I was surprised to find that I wasn't
hard.  I had never even really considered this happening: the other times I'd
had sex with her, everything had happened without thought or effort, more or
less.  I tried to get myself hard for about thirty seconds, feeling more and
more abject, as Marie looked back at me.  Finally I gave up, hating myself for
giving up, and threw myself down on the bed next to her, hot tears in my eyes.

Marie seemingly ignored me for a while. Then she ran her hand through my hair.
I can't remember what she said, or if I said anything.  Before long we fell
asleep, together.

When we awoke I felt calmed and drained.  The shame of the night before would be
something I'd deal with later, I figured.  Brunch with literary people and the
reading were going to happen that day.  Marie woke up and we talked in bed,
mostly about literature.  She seemed to want to talk about my writing.  "You
should make a chapbook," she said.  I figured she was being sincere.  

``I don't think my writing is good, right now,'' I said.  I hoped that I would
soon not feel like this, that I would soon have a chapbook and I would have
something to my name.

``You need to stop worrying about making yourself look good in your writing,'' she
said.

\chapter{IMAX and tumblr} 
I felt strangely, deeply exhausted.  On Metro North I wrote short poems with the
words heavy on my mind and posted them on tumblr.  The men and women
riding the train looked different to me, now that the summer was over, 
in the early afternoon.  My consciousness flickered intermittently; 
I drank the Vitamin Water "energy" flavor.

I wondered if this new feeling would last.
...
I wondered if this new feeling would last.

  

\chapter{Real Life} 

Throughout the middle half of college, the concept of ``real life'' was
important to me.  I felt that ages 18-20 had been a series of almost
uninterrupted crises, and that I hadn't had a chance to build or live in any
sense.  Instead of girlfriends, I had fucked people from Internet for a week and
never seen them again.  I had created nothing, only learned and moved and
wasted.  ``Real life'' became a self-conscious fantasy that involved
timelessness, progression towards a goal, sanity, happniness, and certain
situations of the physical world of life.  I thought of a certain overcast
Sunday in Taiwan when my host parents took me and a German exchange student to a
pool club on the top of a skyscraper.  The place was pleasant and decorated for
Halloween.  I did a few laps in the pool, and then talked about amorphous career
and international things with the German student.  He always feigned surprised
at many things I said and would say "sorry?".  I'm not sure where our host
mother was during all of this.  It was a very grey day and the club and building
were almost all white, except for the dark blue room reserved for the hot and
cold water baths.  I went into this room alone and was in the hot room when an
older Taiwanese man started making an effort to show me how to wash myself with
the pumice stone, which eventually escalated into him scrubbing my balls, which
obviously made me uncomfortable, but I put up with it.  Eventually the host
mother picked us up.  On the way home, we stopped for Italian food.  I came to
love the Taiwanese approximation of Italian food more than ``real'' Italian
food.

The fantasy of real life was strongest when I returned to Cornell in 2012.
I felt I was ready to get into a grind that would take me somewhere I couldn't
anticipate, a place of beauty and continuity.  

\chapter{Casual Sex}

There was a storm in the late afternoon the day before Marie left New York.
When the storm came all of the people in the office went to the windows to
watch.  I found this charming and romantic and gave up on work for the day, but
stayed late nevertheless, until after most other people had gone and the
office's air conditioning had been turned off.  

I thought back to the night before, when I'd had dinner with Marie.  It had been
very unsatisfying.  We met in Union Square and went to a Japanese restaurant,
for lack of something better to do, and talked about the usual stuff.  Marie
used my phone to try to arrange her last twenty four hours in the city.  At some
point it seemed like she tired of me and was ignoring me.  For some reason,
possibly due to the humidity that would eventually build into the storm of the
next day, I felt insane and used my chopsticks to drop my wet tofu onto the
plastic placemat she was staring at.  It was an angry gesture and it made Marie
angry.  She told me she felt disrespected and left a few minutes later.  I
wondered if it'd be the last time I saw her.

I realized that Marie had forgotten to log out of her facebook on my phone.  I
considered logging her out, but then decided against it.

I wanted to have sex with Marie again.  My feelings towards her were stale and
confused, but I felt more sane and powerful than I did in February, and I didn't
want her to ignore and forget me now.  Sitting in the empty office, I read
through her recent messages, making sure she didn't have plans, and then
messaged her: "ur mad at me but do u want to have sex."

I had a mental image of face-fucking her and doing exactly what I wanted.  I had
never quite done that before.  I thought back to ??? and how I had desired sex
on a sunday afternoon with plenty of time and without any context.  

I sent her another text: "it will be good".  Marie responded, asking where and
when.

\section{}

An hour and a half later, Marie arrived at the lobby of the Radisson.  She
smiled and touched my arm, and then followed me into the hotel bar.  

Marie wanted a Bloody Mary and I ordered it for her, getting a water for myself.
I felt slightly self-conscious with Marie, she was wearing the GABM baseball cap
and didn't look too good.

She started up the conversation: her publisher was going to pay for her book
tour, and Glamour was going to do an article on her.  This was the stuff we were
talking about the night before.  

"I'm not surprised," I said.  I felt proud of her.

Marie's voice was barely audible in the loud Midtown bar.  She said something
about not putting on makeup.

"I can't really tell the difference," I said tiredly, thinking that her skin and
lips actually looked fine.

"Look at me," said Marie, after a second.

"What?" I said.

"Look at me."  She was smiling a bit.  She slapped me, with force.

I continued to look at her for a few seconds, then looked away.  No one at the
bar was looking at us.

"Don't do that again," I said quietly.

"Don't insult me again," Marie said.

"When did I insult you?"

"About my clothes, and my makeup..."

"I didn't mean to insult you," I said, after a moment.  I was thinking about how
maybe I was going to regret this whole thing.  Marie slipped off her barstool
and walked away.

"Where are you going?" I said unemotionally, but she was gone. 

The barman gave me some Chex Mix.  I used my phone to figure out how to cancel
the hotel room.  (It had free cancellation.)  I considered running after Marie,
but I realized I still had to pay the bill.  And, I'd be okay.  I was going to
take the train home, maybe exercise, go on the Internet, feel a little more sad
and stupid, but I'd wake up the next morning for work.

Marie sat back down a few minutes later.

"Hi," I said.  I felt better.

"Hi."

A minute passed.  I chose my words.

"When I said I couldn't tell the difference, I thought you had said that you
hadn't put on makeup...you look good."

She smiled.  I wondered if she was taking what I was saying at face value.

"Is the room like ready now?" asked Marie.

"Yeah, probably."

\section{}

Marie lay on the bed looking at the room services menu while I looked out at the
city.  It was still light out.  

"Don't order yet," I said.  "I have to leave for my train."

She put down the menu.  I paced the room, then took off my clothes except for my
socks, and joined her on the bed.  Marie lay there.  I was silent for a moment,
then placed her hand on my penis, and she moved her head to give me a blowjob.
I thrust into her face, moved her head.

When I pulled away, she inhaled sharply, and I was surpised.  I felt sort of
exhilarated and kissed her, but her mouth tasted sour and I didn't kiss her
again.  I slowly undid the buttons of her shirt and pulled it off, and then
pulled off her shorts.  I paused to look at her pubic area fully, and then
inserted into her inexpertly.  

She gave me head on her knees.  Her eyes were closed and I forced them open with
my fingers for a moment.  She struggled her arms for a moment and then stopped.  

At one point, shortly before I came, I watched her stomach contract I thrust,
not wanting to come, I realized that this experience was definitely worth it.

I came over her neck and collarbones, it felt good.  I got her tissue paper from
the bathroom.

\section{}

I took a short shower.  It felt good to close my eyes and feel my hair become
wet.  The bathroom was decent and it had gone ok.

When I got out, I consulted with Marie and ordered room service, then lay down
on the bed.  Marie lay her head on my shoulder.  This didn't bother me at all.
We watched the Olympics coverage for about twenty minutes.  After room service
came and I ate my burger, I got completely dressed.  

I pressed my face into the bed for a few minutes, then got up.

"If you ever need anything," I said, "hit me up."  Then I left.

\section{}

The next morning on the train, I read through Marie's messages.  It was a
tedious process on my blackberry and the phone became very hot. 

The first thing that became apparent was that two British guys came over
after I left, and they had a threesome.  The threesome had been somewhat
disturbing.  As a footnote, she noted to her friends that she had slept with me
and that it hadn't been good, I had done lame forced dom stuff.

I didn't really care about the fact that the dom stuff had been lame and forced,
I had enjoyed it.  But I felt sad and empty seeing confirmation that I was a small part of
Marie's life, that there was always more exciting more intense and literary
stuff happening to her.

I continued searching for my name, and didn't find much.  There were some
messages after the party, where Marie was talking to Evan, someone who followed
me on Tumblr.

"I was disappointed with Patrick, he was boring," said Evan.

"Mew," said Marie.

I felt angry.  Evan was boring.  I was not boring.  It would show in the long
run. 
            
\chapter{Hyatt 48 Lex}
Beach House concert at the beginning of summer

I felt strangely, deeply exhausted.  On Metro North I wrote short poems with the
words heavy on my mind and posted them on tumblr.  The men and women
riding the train looked different to me, now that the summer was over, 
in the early afternoon.  My consciousness flickered intermittently; 
I drank the Vitamin Water "energy" flavor.

I wondered if this new feeling would last.
...
I wondered if this new feeling would last.
