The flight to China was long enouhg for me to feel like I had always been on the
plane.  During a darkness that made no sense as night, after I had watched two
movies, the seatback display showed that we were flying over northern Russia.  I
rested my head against the cool window, trying to understand the lights below.
The hexagonal lines and clusters were gradually washed out by the early morning
grey of snow.

A driver and his wife were waiting for me in Shanghai.  We drove accross the
longest bridge in the world, which had opened a few years ago.  There was a rest
stop at the midpoint of the bridge, about 12 miles out in the middle of the
Hangzhou bay.  The driver asked if I needed to use the bathroom, and I said yes.
I felt unsteady when I got out of the car, watching the ocean swells against the
pylons below.  The bathroom had squat toilets and a sweet, rotten smell I
remembered from some parts of Taipei.  I looked at myself in the mirror.  I was
wearing a blazer, and my face was red from the humidity and heat.

It was not my first time in mainland China.  As a freshman in high school, I
went on a business trip with my dad and the owner of his company.  The daughter
of the owner also went on the trip.  She was a freshman at art school, a tall,
smiling young woman.  I was fascinated by her and the situations we found
ourselves in: visiting freezing factories where old ladies wore wire mesh gloves
to handle sharp materials, or walking around the world's largest mining trade
show together, climbing over large drilling machines and talking to their
salesmen.  I felt infatuated with her and wondered if it was at all possible she
was interested in me.  I masturbated in the bathroom of the nice hotel my dad
and I were staying in, after the tow hour drive through Shanghai traffic.

After we crossed over the bridge we entered a flat marshy area with many rice
paddies.  I continued to stare out the window, sometimes taking out my
Blackberry, which didn't have data.  I saw a young man wading through a flooded
field, carrying a green head of cabbage.  The water reflected freshly-poured
concrete.  

The Gerber factory was located in Ningbo, an industrial city on a river,
somewhat close the the ocean.  A squat man in a buttondown shirt greeted me when
the car pulled through the gates of the factory.  He showed me to my room on the
second floor of the office.  I tried to talk to him in Mandarin without much
success before he told me that he was Japanese and only spoke a little bit of
Chinese.

Going to All the Restaurats My HYP Friend Reviews on Yelp

For a brief period after I returned from working in Chinese factories, I had a
pretty brutal worldview that placed the accumulation of raw wealth above all
else.  During this time, I tried to surround myself with more privileged,
ambitious people.  I was successful for a while.  I made dinner plans with old
friends who I suddenly saw in a new light, dressed well, and read a lot of blogs
about finance.  Through visits to to Cambridge and New York I managed to build
uneasy friendships with internship-obssessed students with 500+ connections on
LinkedIn and a love for success.

Eventually the mindset created by observing freezing cold garmet factories
dissipated, and I returned to more normal American fuccboi/softboy type
obsessions.  I lost interest in my aggressively acquitistive friends at Harvard
and UPenn.  Their business-casual lifestyle seemed somewhat boring and very last
year, and I told myself that I wasn't jealous of their internships at Bain
Capital, the Huffington Post, Google, etc.

It was only this fall, as the weather started to get cold and I continued to
work on unimpressive freelance web development projects, that I started to view
the Snapchats and Instagram posts of my former friends (now acquaintances) with
jealousy.  It was obvious that their postgrad life was faster than mine.  Had I
screwed up somewhere, or more likely, just not been up to the par required to
get a job and keep this kind of company?  Was I too ugly and awkward?

I suppressed these feelings.  I knew it was likely a facade.  But I had a facade
too, and mine was much less fun.  Whatever my literary and cultural interests, I
wanted to WIN and go the clubs I didn't go to, because I told myself I was
"allergic to exclusivity".

One evening, after I finished a day of mostly procrastinating at my coworking
space, I looked for a nearby bar on Yelp.  I normally went straight back to
Bushwick at the end of the workday.  I selected a bar/cafe a fifth of a mile a
way, with three dollar signs that supposedly ``oozed ambience''.  I saw that one
of my old friends from 2011 was the top review.  She praised the date cupcake
dessert, and gave the place four stars.  This friend, named Rachel*, is a
consultant at McKinsey*.  Her yelp profile said that she was an Elite '15 for
New York City.  We had kissed before at a HYP party, and then tried to get into
another party.  When I was unable to get in, even after she told the brothers
that I went to Cornell,  she and her girlfriends apologized and said they were
going somewhere else, and ``it's already late, isn't it?'', leaving me in the
Februrary cold.  At the time, I didn't let it bother me.

I decided to go to all the restaurants that Rachel had reviewed in New York, to
try to get a feeling for what her life was like.

Here's a list:

1. Moto Cafe, Williamsburg:
These restaurants created a very strong temporary feeling of peace and romance.

Sometimes after work Ion my bed and grinned uncontrollably, thinking about
the money I was making.

It was dangerous to lay on my bed and think about myself.

I felt good in the morning, usually. Before I went to sleep, I opened the
blinds. My room had a very clean wooden floor that's warmed by the morning sun.

There is a certain part of me that always wanted discipline and order,
wanted to be organized and strong. I wanted a situation that would force me
to live properly, and I had failed to find it.

I'm better at bullshit, I realized. I had lost my ability to bullshit during my
first semester at Cornell, and I had been living in constant retreat since.

Breakfast was sort of like a meeting. I reported the information, prices, etc
that I got from America the night before, and offered my suggestions. Often we
discussed things for an hour or so, drinking coffee. Outside the window, the
workers were riding into the factory on scooters and bikes, checking in with the
security guard.

Sometimes around midday I thought silly things like "I'm going to the bathroom
and there I'll think really hard, and after that I'll just try to live the best
life I can and not worry about existential things."

There was a Japanese "technical advisor" living with us. He was in his sixties.
I appreciated his taste in aesthetic experiences.  After dark or early in the
morning, we would go on long cycling tours of the surrounding area. He owned a
pair of excellent racing bikes.  There wasN nighttime traffic, sprawling new
apartment housing developments, rice paddy canals, etc.  Asiatic cows.   It was
nice to appreciate these things with someone else.  One night there was the
moon.  He didn't speak English, and his Chinese wasn't very good.

I imagined buying an extremely clean apartment and furnish it simply and hiring
someone to clean and cook.

I felt calmer.  I had work and money, but not self-control.  I didn't live
regularly.  My social skills were somewhat improved, but only in a
Chinese/Japanese context.

"hmm what did we talk about back when we talked"

The day's work was done at 5:30, and we went upstairs for dinner.

Hirata said: "I like rich people. I don't like poor people."

~

Elma and I went to the customer's factory. All the other
engineers underestimated Elma because she is a woman and ugly. She made \$270 a
month. We walked into the room where they were sewing. There were about three
hundred women operating sewing machines. Elma said haoduomeinv.  (look at all the
beauties)  They were all mother-aged. It was loud and they were playing Teresa
Teng over the loudspeakers. It smelled of sweat and fabric. I felt lightheaded
but the music made me happy and I felt invigorated or something, like I had
just washed my face.

easy to romanticize with the largeness of the machinery and the weightiness of
the product. The area we live in smelled like freshly-machined steel.

Elma did a good job getting the marker files we needed and now I think we are
friends.

I explained the concept of wage slavery to Joy as we walked.

"like how he talks about wage labor, like earning the money and then spending
it on food (lattes and pizza) needed to repair/replenish my body for another
day zzz this is like everyone of course, but that thought/concept keeps running
through my head."

So that day I was in a bad mood when we returned to our factory. But then
Japanese boss called me into his office and gave me the first envelope with
"unoffical lifestyle fee". I ran upstairs and counted the brand new bills on my
bed.  Thousands of dollars.  Then we all went out for Japanese food at the
Westin hotel downtown.

I was very happy.
