``I'm interested in spending a semester or two at like a state school,'' said
Samuel, a few days after Christmas.  ``Do you think I'd be able to get credits?
I don't know if this makes sense.''

``Seems like a good idea to me,'' I said.  I was lying on my bedroom floor,
cooling down after a workout.  

``I can't really articulate why I want to go to state school while still
graduating from Brown.   Maybe it's intuitive, the reasoning behind it.'' 

``No, I get it,'' I said. 

\plainfancybreak{12pt}{2}{* * *}

A few days later, I flew to Seattle for a software engineering interview at
Amazon.

When I got to my hotel, it was warm enough to sit outside in the dark and do
some coding problems.

My phone flashed.

``I'm considering taking another class to increase the chances of being able to
go to state school,'' said Samuel.  

``How do you feel about writing a few papers and blog posts?  For ... \$1k?
Basically, you'd be taking the class for me.  Do you want to pursue this?'' 

I stared at my phone for a moment, thinking about the coming semester, and then
said ``sure''.

\plainfancybreak{12pt}{2}{* * *}

The next morning I woke up feeling intuitively sad, and walked to the Amazon
campus.  About thirty of us were shown into a large conference room, split into
groups of three, and given laptops.  I tried to be social with the other
interviewees, despite the nervous pre-interview silence.  I was always reminded
of soldiers standing in a landing craft.

As we booted our machines, a proctor gave each group a laminated booklet
detailing a programming challenges.  We were supposed to work together.

``You have until 3pm to finish your implementation,'' said the head interviewer.
``You'll each submit your own version of the code the repository listed in the
booklet.''

I momentarily felt a blind, helpless rage at my situation, and imagined standing
up and walking out of the interview.  I wondered what the consequences of that
would be.  

After a minute of this feeling, I smiled at my teammates, and started to read
the problem.

\plainfancybreak{12pt}{2}{* * *}

After the interview, I fell in with a group of the more confident, social
interviewees, and went to an atmospheric Asian restuarant in Belltown.

A guy from McGill, Saurabh, was showing me his mobile-optimized graphics engine.

``It's really close to the metal.  To optimize for mobile, I had to directly
open up buffers for matrix operations.  Cool stuff.''

A waitress brought us warm saki and sashimi, and we talked about our other
interviews.  All of us had interviewed at Facebook, some of us at Google.  

I smiled at myself in the bathroom mirror after pissing.

One guy, also from Cornell, told us about his genius boss at Palantir.  They had
done acid together, at work.

``That's terrifying,'' I said, picturing Palantir's glossy black office in
Chelsea.  I rested my face on my hand, thinking of Chelsea Manning alone in
Iraq, talking to anyone she could find on the Internet.

\plainfancybreak{12pt}{2}{* * *}

After dinner, we decided to go to a legal recreational marijuana shop, the first
and only in Oregon.  I felt slightly ashamed when the cab driver knew exactly
where we wanted to go, but purchasing legal weed was an amazing experience.

We went to a park near our hotel.  By the time I finished my pre-rolled joint, I
felt pretty high, but not paranoid or dysphoric.  The other guys were stupidly
high. 

Saurabh stared at each of us with wide eyes.  ``Do any of you guys feel that you
might not die?  Like, you might live forever because of computers,'' he said.

The sober Taiwanese guy laughed manically.  I smiled and listened to the wind
above.

``Like from stuff I've read, Amazon Web Services is alive, in a way.  It does
homeostatis.  And if we get offers from Amazon our code will become a part of
it.''

I thought about the Palantir office again.  The other Cornell guy was rocking
back and forth.

``People who don't understand computers are going to be fucked,''
said the Cornell guy.

``Yeah, they're fucked,'' said Saurabh.  

``Have you guys spent all of your food allowance?''

``I don't know,'' I said.

\plainfancybreak{12pt}{2}{* * *}

The next morning I woke up early for a jog.

I had a bit of a weed hangover, so things felt surreal.  It was still warm,
however.  I ran downhill, towards the ocean.

At the harbor, the horizon seemed close.  I walked along the boardwalk and
watched glassy bubbles well up in the green water.  I thought of the programmers
at Microsoft working in this hydrated environment. 

I took a picture and texted it to my mom.  I thought about it for a moment, and
then told her about the legal marajuana shop.  She didn't respond, which I found
both funny and concerning. 

I started to jog again.  The interview had gone well.  Assuming I got an
offer from Amazon, I'd move here. 

\plainfancybreak{12pt}{2}{* * *}

It was bitterly cold back in Ithaca.

Before my first class, I went to the erg room for forty minutes of steady state.
I felt hopeful and clear-headed after, showering with my teammates.

When I returned to my locker, there was an email from my Amazon recruiter.  My
heart beat rapidly and my throat constricted.  "Thanks From Amazon" was the
subject.  It was a rejection.  What the hell, I thought percussively. 

I threw my phone onto a stack of clothes and started to get dressed.  I'm
totally willing to be in denial about this, I thought.  It doesn't make sense.
Unbelievable. 

\plainfancybreak{12pt}{2}{* * *}

In my human-robotics interaction class, the professor told us to find a partner,
and then gave us five minutes to build a tower out of spaghetti, string,
marshmellows, and tape.  It was a competition.

My partner was one of the few non-Asian women in the class.  She had a blemished
face and seemed to be almost thirty.  We instantly began to have difficulties
planning of our tower.  

I wanted to incorporate the string, but she didn't think it'd help.  At some
point we just started to build, and ended up with a tower that was probably the
second tallest in the classroom, until it broke at the last second.

We joked uneasily, but it was obvious that we were secretly blaming each other,
and took these things seriously.

The professor told us that groups of kindergarteners typically built the tallest
towers, besides engineers.

\plainfancybreak{12pt}{2}{* * *}

On a Saturday night during a snowstorm, I went to the library and checked out
``Dangling Man'' by Saul Bellow.  It was the first book for Samuel's class.

The main character did all of the unlikable, confrontational things I did in my
bad dreams, where I screamed at all of people in my life.  In these dreams I
often quit things, saying that I never really liked rowing anyways, and then
endured a deep, lucid regret that didn't go away until my alarm went off.

\plainfancybreak{12pt}{2}{* * *}

By February I was back in the Cornell cycle of hypomania, time debt, failure,
fatigue, and Internet.  When I started college, I tried to change my habits and
become the beautiful, strong, good person I wanted to be.  But it seemed the
only way I made any progress was simply sucking it up and accepting the cycle.

I still wanted some sort of catharsis, though.  I told myself that rowing was
the most important thing.  Last one, fast one.  The early winter workouts were
very long, but not particularly stressful or painful.  I was getting a pretty
consistent 6.5 hours of sleep.

Every day I visualized finishing my last race and lying down in the boat.

``I'm going to need a lot more attention, love, and respect!'' I wrote in my
notebook. 

\plainfancybreak{12pt}{2}{* * *}

On Valentine's Day we did the `massacre', a 10k erg followed by a 3 mile run.
It was never that bad; it was relatively easy to find a consistent level of pain
pain in the cold without much suffering.  

After spending the rest of the day in bed recovering, I went to dinner with my
partner from robotics.  Her name was Allison.  We'd chosen to work together.  

Right after Allison and I sat down at our table, a small group of upperclassmen
rowers came in with girls.  I nodded at them over Allison's shoulder.  

I was happy that we'd picked the same restaurant.  I was proud of how civilized
they looked and acted, much better than most Cornell undergraduates, who seemed
to lack a critical sense of \textit{noblesse oblige}.

``Have you seen the brushes that they use on cows?'' said Allison.  We were
discussing ideas for a robot that could be used in commerical kitchens, our
first assignment.

``No,'' I said.

``They give cows these large, mounted, spinning brushes. The cows love pressing
up against them, and it increases milk production.'' 

``You mean we could make something like that for dishwashing?''

``Yeah,'' said Allison.  ``I feel like it'd be helpful.  I could test it out,
I'm actually working as a prep chef right now.''

``Oh yeah?  I did that for a while.  It was okay, but I always smelled like
grease after.''

After eating, Allison and I went to the bar next door for a drink.  We started
talking about tech companies, and she asked me about my post-grad plans.  

``I'm not exactly sure yet,'' I said.  ``Probably Amazon, if I'm willing to move
out there.''

``Cool,'' said Allison, nodding.  ``I think that's where I'm going to move,
too.''

``You got an offer somewhere on the west coast?''

``Yeah, at Google Research.''

``Awesome,'' I said.  ``Working on what?''

\plainfancybreak{12pt}{2}{* * *}

Practices became harder.

I was having trouble pushing myself.  When I was 20, during a tough workout
sometimes the right song would come on, and I'd feel a trickle of cold
adrenaline and want more.  Something about the awful situation made me embrace
it, despite the urge to look for a way out.  It had been a broken feeling, but
it was fast.

Now some part of me just wanted it to be over, for someone to call it off,
cancel the race.  This was an ugly old feeling from childhood.

\plainfancybreak{12pt}{2}{* * *}

The weekend before dry season, I drove a group of people up to the rowing house
on North Campus.

When I arrived, Tom introduced me to my date from Tri-Delt.  We said hi.  She
asked me how drunk I wanted to get, on a scale of one to ten, and I said eight.
She said eight was a good number, and we did shots.  Then we sat down for
dinner.

As we did dishes, other people started showing up.  It was mostly people I
recognized from other rowing parties.  

My date and I stuck together, wandering around the crowded house. It was a nice
change from how I normally felt at these parties: ignored by non-rowers, and
darkly motivated to train harder, so I'd get more respect from my teammates.

When it started snowing around midnight, we went outside along with almost
everyone else.  It wasn't very cold.  Some freshmen from both teams were naked,
running laps around the house.

I put my arm around my date, feeling validated by the beauty of the moment.   I
made sure to appreciate the long, straight country road on the opposite side of
Lake Cayuga, and the suggestive condensation on the windows of the house.  I'd
felt this many times. 

We went to the tree line and made out.  Her saliva had a strong taste, typical
of Cornell.

An injured rower from my year invited us up to his room, where we did lines of
coke supplied by a pretty lightweight. 

I was impressed by the amount of vaporized smoke in the room, and the mature
hedonistic feel.  

Then we went back downstairs to dance, now very fucked up, in a sort of stunned
way.  

While we were dancing, someone threw a heavy glass beer boot on the brick floor,
and it shattered.  A tall Asian guy was standing at the door with his fists
balled up, staring down Tom, a quiet, sardonic rower, also from my year.  

``Oh shit,'' I said quietly, as I was pushed away from the glass by Andrew, who
was yelling ``woah, woah, woah''.  Tom stepped around the glass and lunged at the
Asian guy, who backed up. We followed them outside.  The snow had stopped.

``Why is he fighting here,'' I said.  ``There's no way he can win.'' 

The Asian guy took a few steps towards Tom, raising his hands.  He was
expessionless.

``You're a fucking pussy,'' said Tom, smiling. 

The Asian guy swung at Tom, the second punch hitting above Tom's eye.  A 230lb+
sophomore came running of the house and executed a wrestling takedown, putting
the Asian guy into a headlock and screaming at him.   Now the whole house was
standing on the porch, some laughing and some concerned.

The commodore of the heavyweight team appeared and helped the sophomore walk the
Asian guy away.  We helped Tom put a rag on his bleeding eyebrow and sat with
him.  

\plainfancybreak{12pt}{2}{* * *}

When the house was almost empty, my date and I agreed to leave.  We walked
silently across the suspension bridge to where she lived in Collegetown.  I felt
a pressure, trying to think of something to say.

She shared a suite with some other women from Tri-Delt, who were still up.  In
her room we took off our clothes and starting kissing on the bed.  She got up
and turned off the lights.

``I can't see,'' I said.  

``Yeah,'' she said.

We kept kissing, and I took off her bra.  I'd imagined hooking up with someone
from a rowing party many times.  We moved our hands downwards and I started
fingering her, listening to her breath.  Time passed.

``Pat, stop,'' she said.

``What?'' I said.

``You're not hard, Pat,'' she said.  Her hand was on my dick.  I stared down at
her eyes, glowing softly in the dark.  I started to kiss her again.

``Stop, you're not even hard,'' she said.

I stopped, still on top of her, looking down.

``Pat...'' she said.

``You're so gay, Pat,'' she said.  ``It's okay, my best friend is gay.''

``No, I'm not,'' I said, after a few incredulous seconds.

``Oh my god, yes you are.  You're so gay.  You like Tom, right?''

``What?  I'm not gay,'' I said.

``Okay, bi, then?  I could tell you really like Tom.  It's okay.''

``I don't know,'' I said.  ``No,'' I said.

I got off of her lay on my back.  A minute later she went out into the hall, and
then came back in and told me to get dressed.  I started to feel distantly
upset.

She walked me to the door, telling me that she adored me.  I apologized.  As the
door closed I heard her saying ``oh my god'' to her suitemates on the couch.

I stalked home blind drunk, feeling increasingly upset and letting my body go
slack against the cold wind.  Back in my room, I realized that I'd left my watch
at her place.  I wouldn't be able to ask for it back.  I let out a noise and
punched the wall. 

I hated that watch anyways, I told myself. I had been pressured into spending
\$500 on it by my grandfather.  I facebook messaged an Internet girl while
writing into a Google doc, mostly in all-caps.  Then I put myself to sleep.

\plainfancybreak{12pt}{2}{* * *}

The next morning I woke up without a hangover, and jogged to North Campus to get
my car.  

The first essay for Samuel's class was due.  It was time to change my life.  I
wrote the first third of the essay before noon, writing about Joseph's doomed
rejection of the `code of the athlete'.

I went to a dining hall for lunch, and worked on my scalable systems assignment
while reflecting on what I wanted in life.

It seemed that at a base level, what I wanted most was a brand-name job at
Facebook, Google, Amazon, Goldman Sachs, J.P.  Morgan, etc.  I wanted the
feeling of success that would come with such a job, and the six figure salary.

I continued this line of thought during yoga class, necessary for the coming
week.

It would be the easiest way to fix my life.  I knew it probably wouldn't
\textit{actually} fix my life.  But from my parents perspective, from everyone
else's perspective, it would.  

I wanted it more than I wanted the dismal, self-delusional success that I might
find in writing or game development.  It was the most pure thing to want. I
wanted it the way I wanted to hook up with hot, normal college students, for the
same reason that Samuel wanted to go to state school. 

\plainfancybreak{12pt}{2}{* * *}

At Monday morning lift, we were told to warm up for a max squat test.  Tom and
Charlie came over, Tom grinning widely despite his swollen and grotesque eye.

``Yo, Steadman, how was it with uh, Jennifer?  She was all over you,'' said
Charlie.

``I don't fucking know, man,'' I said.

``She like, told us that you were bi?  What?  I was like Steadman?  No.''

``Yeah, noo,'' I laughed. ``I was just really fucked up.''

We stopped talking while the weight room coach gave us the standard instructions
for the squat test.

``Yeah, she was telling us...she said you said you were bi.  I was like
Steadman?  I don't think so.''

``I have no idea what the fuck I said.''

``It didn't seem like you really liked her that much,'' said Tom.

``Yeah, nah,'' I said.  ``Good times though.''

``Yeah buddy,'' said Tom.  ``Crazy night.'' 

We went to find appropriate spotters for the test.

I did well, putting up some of the most weight on the team.  In the locker room
people asked me how much I had squatted and were impressed.  I felt optimistic
about my chances for the season and went to Uris library to take a nap before my
first class.

I felt good.

During my first few months on the team, I'd experienced a constant sense that my
teammates were calling me 'scrub' or 'bitch' behind my back.  I imagined that if
I ever showed my 'true self', their friendliness would turn to open hate.  I
imagined it would be like killing allies in a video game and having them all
instantly attack you, your crosshairs going from green to red. 

\plainfancybreak{12pt}{2}{* * *}

I stayed up late to finish Samuel's essay, mostly procrastinating before I
finally went into the cave.  I ended up finishing at 3:30am.

This messed up the rest of the week, a prelim week.  I got somewhat sick,
possibly due to the polar vortex.

I emailed coach to tell him I had a fever and wouldn't be at practice, and then
met Allison at the robot lab to merge our teleoperation code.   Allison's code
was non-functional overall but included a bit of linear algebra that corrected
an issue I had with negative rotations for the robot's arm.

Around 1AM we walked home together, both shivering hard.  I felt lightheaded,
but happy to be talking to Allison.  I stopped at Collegetown Bagels to get some
protein shakes and Gatorade.  It was full of drunk people.  I felt sexually
frustrated, but mostly tired.

\plainfancybreak{12pt}{2}{* * *}

Things always seemed better when I was in control of my behavior.

We did bracket racing on Saturday morning.  It was sunny and warm.  That
evening, an injured rower came over and I installed ``Deus Ex'', a video game
highly recommended by 4chan.   On Sunday I went to yoga with a friend who I
still kind of wanted to date.

My quads felt large and hammy.  We were surprised by an easy workout Monday
night.  It was warm and we jogged to the Cornell plantations.

The big issue, I thought, was whether or not I would live out my life dreams.

\plainfancybreak{12pt}{2}{* * *}

For my 23rd birthday, I had dinner with my parents at the hotel school
restaurant.  I told them I was evaluating the Amazon offer, but was more
interested in other options.

In March, the new Drake album came out, and I listened to it walking
to class, feeling a dark euphoria.

This hypomania had been the one constant of my time at Cornell.  In the fall of
2013 this had led to a very strange form of depression, when my life was falling
apart but I felt very good because I was going to practice twice a day, eating
well, and showering.  Eventually I signed up for a Gannet psychiatrist, who
prescribed an antidepressant and told me to drop some classes.  This fixed
things, basically. 

We had our first 2k test.  It went well.  I went into the pain cave at the right
time, with about 800 meters to go.  I rowed reasonably well as my vision went
yellow, and was able to sprint.  

``Wow, Steady, looks like you're going to PR this year,'' said a rower from my
year at dinner.  

The post-2k feel was wonderful, as always.  Some girls came over and we played
records on our record player.  

\plainfancybreak{12pt}{2}{* * *}

During the week before spring break, the inlet was still choked with ice. We
drove twenty minutes up the lake to where the water was clear.  The practices
were long and frustrating.

Thursday was sunny but cold.   My housemate Max drove us up the lake after
class, so we could leave right when he got off the water.  I had a release due
for my game development class the next day.

Coach had us doing five minute pieces against the 3V, starting half a
length up on them.  No one seemed very motivated in my boat: it was a weird
mixture of bright, windy, and cold, that felt like skiing weather.

After a few bad pieces, Coach drove over in his launch to talk to us.  When my
pair was out, I stuck a hand down under my balls to try to keep my fingers from
going numb, which made it hard to control the oar.

``How's it going guys,'' said Coach.  Joe said something about the boat not
being set.

``It's not enough,'' said Coach.  He pulled his launch back around towards us,
against the wind.

``Let me tell you about the 2010 varsity.  That boat wasn't really anything
special, but boy did they work hard.  I talked to Joe Vaughn a few weeks back
and he told me how they went to a deep dark place to win it.''

``Do you guys want to win?'' said Coach.  ``Yeah Coach,'' said someone.

``You win a race like the sprints, you walk away different.  You might not look
any different, but you walk away a different man.  Alright, get at em.''

We did a few more pieces which went worse.  I didn't get any feeling of torque
or swing.  

It was still fully light out when Coach told us to dock.  The coxswain fucked up
and we were blown into into the rocky beach.  I sculled Max's blade, but the
boat was stalled.

The coxswain muttered under her breath.  She was the hot coxswain, but no one
respected her.  Eventually we agreed to get out of the boat and wade it in,
slipping on the rocks.

My socks started to freeze as we tied the boat down on the soggy grass.  I shook
the seashells out of my leather boat shoes, sitting on Max's bumper.  It was
another absurd practice.  

I warmed up during the silent ride back to campus, and left my ruined shoes
outside of my apartment.  

On my way to the Computer Science Undergraduate Lounge, I got two RockStar
energy drinks and a chicken parm.

Most of my game development project team was there.  For a while, we all worked
quietly.  I was finishing up the death bounding box for the level.  Ivan and
Joseph were talking about the memory leak.

``About 300 megabytes on each level load,'' said Ivan.  ``Christ,'' I said.

Mentally I imagined 300 medium-length novels.  I kept working with Ivan until
the 10AM class, when we presented to the professor.

\plainfancybreak{12pt}{2}{* * *}

The next day, I slept deeply from one to four in the afternoon and then went to
practice.  It turned out to be a relaxing 3x30 minutes of steady state.  It
was warm enough to run outside, and it was still light out.

I felt lightheaded.  When I got home from practice, I began to feel the immense
relief of spring break.  But, I knew I was sick.  

I struggled through practice on Saturday, going to Gannett in the afternoon.  I
had pneumonia.  I emailed the coaches, saying it might be a few days before I
could practice.  

At the 7/11 I got as much food and beer as I could carry home.  I decided I'd
give myself a day or two to recover.  I started to drink and play Deus Ex.  

I did this for three days.  My pneumonia got pretty bad, requiring me to go to
the bathroom to cough up bile.  I felt guilty about not being at practice, but
it was okay.  I felt more guilty about not working on my game project. 
 
I played Deus Ex late into the night, my space heater at my feet.  I got so
drunk that the display swam in front of me.  The 2001-era graphics seemed
impossibly beautiful.  

When I drank wine or beer in Deus Ex, the screen got more and more distorted,
the effect stacking with every drink.  Sometimes it was almost impossible to
tell what I was doing, in the dark underground areas of the game, or stumbling
around my basement apartment, coughing until I couldn't breathe.

It was one of the happiest times I had during college.

\plainfancybreak{12pt}{2}{* * *}

After my sickness, rowing felt like a big nuisance.  I rejoined the team halfway
through break, jogging on the shore to get my lungs back.  

I was still boated for the first race of the season, at Harvard.  My boat
practiced in the morning, when it was dead calm.  The bow of the shell broke a
thin film of ice on the the water, catalyzing an ASMR noise that spread across
the empty lake.   

When I fell asleep in class, or quit early during an extra workout, I didn't let
it derail me for more than a few hours, or at most a day.  I knew that even if I
quit, I could potentially un-quit.  I could always listen to EDM as I walked
between classes to feel a dependable, dark euphoria.
 
The long bus ride to Cambridge and the meals at the hotel gave me time to think
over my life.  Was I a scrub?  It was my first time at the Harvard boathouse.
Inevitably I thought of Mark Zuckerberg and the men who had rowed in this
boathouse, beautiful people. 

We won our race, a long grind into the wind. As my stroke started to fall apart
in the last 500 meters I looked over my shoulder for the finish, the first time
I'd ever done so in a race.

\plainfancybreak{12pt}{2}{* * *}

In the robotics lab, I affectionately watched Allison debug a threading issue.
It was raining and warm outside.  Practice had been really hard, and I felt
myself fading.

``I'm really tired,'' I said to Allison.

``I think I've almost got this,'' she said, highlighting a block of code.

``Push it, and I'll take a look tonight,'' I said.

On the way to Allison's car we stopped at the Mexican-themed bar and ordered
beer.

``Can you believe it's almost over?'' I said.

``Are you excited?'' said Allison.

``So excited,'' I yelled deliriously, suddenly feeling strong emotion.  ``You
must be really excited, right?''

``Yeah.  I've never really left Ithaca.''

``Your parents must be really fucking proud,'' I said, almost jealous.

\plainfancybreak{12pt}{2}{* * *}

During early spring I was usally awoken a few minutes before my alarm by the
sound of my teammates coming down the stairs and getting some breakfast.  I had
developed the habit of waking up around 4:30 AM to drink a Gatorade and eat a
peanut butter and jelly so I'd wake up hydrated and ready to pee, so there
wouldn't be any pressure on my bladder in the boat. 

My boat won easy victories at home against Dartmouth and Syracuse.  I told my
parents to not bother coming to watch.  The next weekend we travelled to
Annapolis to race the Naval Academy.  We were starting to suspect we might be
the fastest fourth boat in the east, a sort of comical, but also exciting idea.
It seemed fitting.  

The water was flat and syrupy, a contrast to the last time I'd raced at
Annapolis, when we shit the bed.  I felt a strong pressure on bladder in the
minutes leading up to the start, and felt very frustrated with the warm up our
coxswain was running.  The Navy boat was mostly scrubby-looking large guys and
one of their stunted male coxswains.

After the sprint we were up half a length, and we walked every time we made a
move.  They didn't make any significant move, even as we passed their docks.  I
heard someone yell my name and felt relief as we held them though the last
two hundred and fifty meters.  It was a beautiful day and even as I recovered in
the bottom of the boat I looked forward the the empty bliss of the long bus ride
home.

\plainfancybreak{12pt}{2}{* * *}

On Sunday, I sat down with a Coors Light and Life cereal to watch the video of
the Navy-Syracuse race.  I felt buzzed and excited. 

My excitement quickly turned to horror.  The video feed still had audio, and
right after the start one could hear Coach Terry say ``We've got to get Steady
out of there, I talked to him and he didn't make a change.''  It was obvious
what he was referring to: I was leaning away from my oar at the end of every
stroke, through the whole race.

It fucked me up.  I knew the coming week was going to be painful and
humiliating: they would try to seat race me out of the boat.

I made myself immediately head out the door to yoga class.  

The thought of not racing again was very painful.  I had always imagined
preparing for my last race: ideally in June, after graduation.

I had imagined waking up one morning in early June, and looking at my body in
the mirror, knowing it was the best it would ever be.  Then I imagined  the
finish of the race, falling back into the fragile boat, my hands slapping the
cool water and my eyes closing, and it being over.

But now it seemed like I wouldn't get that moment.  Or, it had already happened.

After yoga, I didn't feel much better.  I went to the dining hall to work on an
essay for Samuel, but delayed by writing in my notebook about how disgusted I
was by my presence in the world, thinking of my hunched figure in the rowing
shell.

I messaged Samuel, telling him how I felt.

``All of my friends that I admire seem to hate themselves pretty regularly,''
said Samuel placidly.  ``It's something I've come to accept.''

``I don't want to hate myself, it's fucking stupid and I'm sick of it,'' I said.  

Samuel didn't respond.

``Maybe I should just accept the Amazon offer and move to Seattle,'' I said.
``It'll be okay.''

``No, you should move to New York and be glamorous,'' said Samuel.  ``I think
when you look back on rowing it will be very indistinct for you.'' 

Maybe I should have quit two years ago.  I had never seriously considered the
idea before.

``You're living life,''

Surprisingly there was no seat racing on Monday or Tuesday, and I retained my
spot in the boat.  A line squall hit us at the base of the lake, and waves
rolled over the boat as we tried to row back into the inlet.  My teammates were
whooping, and I felt my heart go out to them, for finding this fun.

On Wednesday morning we went out in fours, obviously to seat race.

I looked up at the hills above campus, knowing it might be the last time I rowed
in a serious way on Lake Cayuga.  Then I tried to row well, forcing my strength
into a stroke that would work with my four.  My teammates were quiet, but seemed
motivated. ``Yeah Steady,'' 

I lost by about a length and a half, and when I came down to the boathouse in
the afternoon, we did time trials.  After that, I was on land team unless
someone was unable to row.

\plainfancybreak{12pt}{2}{* * *}

I knew that despite the part of me that wanted to be like these warlike youth,
my equilibrium was being quietly manic on my computer, in the the place I'd
found myself in during spring break.  I cared more for the virtual text of any
given momment than I cared about winning or losing.  I had never really wanted
to exert myself like this, but of course I had been necessary to try.  I'd done
it to prove something to myself and others, and to some degree I'd be
successful, but now it was over and I still felt alone and unsuccessful.

My first day of land squad, I put on my rowing trou and a tank top, but on the
way to the erg room the heaviness in my throat won and I went to the bathroom.
A few lightweights  were still there putting on sunscreen, so I went into one of
the stalls.  Then I willed myself to start to crying, and cried silently, in a
fully warm and cathartic way.  

The end of rowing was more bitter than I had hoped.  It was like many springs in
middle school and high school, when I thought things were changing.  But I had
finished it, I told myself.  I had seen it through, and I had probably done my
best.


\plainfancybreak{12pt}{2}{* * *}

I focused on school, mostly the video game class.

It was like being kicked in the face every day.  I'd go down to practice, row
about 5k with my teammates, stretch or lift, and then go read in the locker
room.  I read a Ben Lerner book.  Sometimes I'd substitute if someone couldn't
make it to practice.

I went to the University of Pennsylvania race as the alternate. 

Classes ended.  For two weeks, I programmed for about 14 hours each day.  

The game came out okay.  It was 3D, and I knew how everything in the game world
worked.  At showcase, I watched a kid with autism beat the final level and went
to the bathroom to cry again, just out of exhaustion.

After the graduation ceremony, I walked out of Schoelkopf stadium, suddenly
unconcerned by all of the other students around me.  I walked straight to where
my parents were waiting.  We got hotdogs and took some pictures.  

``Come back to Donlon with us, we have some presents for you,'' said my mom. 

``Okay,'' I said.  

On the way long walk up to North Campus, my grandfather said something about how
I could start making real money now.

``I'm not so sure I'll be focusing on that, right after graduation,'' I said,
and immediately regretted it, thinking about him at my age, with a four year old
daughter.  My grandfather was silent.  I again had the feeling that my
grandfather despised me, even if he didn't know it himself.  I pushed the
thought to the side.  I was too old for thoughts like that.

Back at the dorm, I opened presents from my aunt and great aunt first.  Both had
given me \$100 checks.  I was surprised and happy.  My parents had given me new
shoes, and would later send me an e-card for \$1000, saying they were proud of
my hard work.  

Finally I opened the present from my grandparents.  The card on the outside
contained a check for \$8000.  

``Thank you so much,'' I said.
