``I'm interested in spending a semester or two at like a state school,'' said
Samuel, a few days after Christmas.  ``Do you think I'd be able to get credits?
I don't know if this makes sense.''

``Seems like a good idea to me,'' I said.  I was lying on my bedroom floor,
cooling down after a workout.  

``I can't really articulate why I want to go to state school while still
graduating from Yale.   Maybe it's intuitive, the reasoning behind it.'' 

``No, I get it,'' I said. 

\plainfancybreak{12pt}{2}{* * *}

A few days later, I flew to Seattle for a software engineering interview at
Amazon.

When I got to my hotel, it was warm enough to sit outside in the dark and do
some coding problems.

My phone flashed.

``I'm considering taking another class to increase the chances of being able to
do the state school thing,'' said Samuel.  

``How do you feel about writing a few papers and blog posts?  For ... \$1k?
Basically, you'd be taking the class for me.  Do you want to pursue this?'' 

``Sure,'' I said, knowing I'd regret it.

\plainfancybreak{12pt}{2}{* * *}

The next morning I woke up feeling sad and walked to the Amazon campus, enjoying
the spring-like weather.  About thirty of us were shown into a large conference
room, split into groups of three, and given laptops.  I tried to be social with
the other interviewees, despite the familiar nervous silence that always
reminded me of soldiers standing in landing craft.

As we booted our computers, a proctor gave each group a laminated booklet
detailing a set of programming challenges.  We were supposed to work together,
but we would submit our own code independently at the end of the day.

``You have until 3pm to finish your implementation,'' said the head interviewer.

I momentarily felt a blind, helpless rage at my situation, and imagined standing
up and walking out of the interview.  I wondered what the consequences of that
would be.  

\plainfancybreak{12pt}{2}{* * *}

After the interview, I fell in with a group of the more confident, social
interviewees, and we went to an atmospheric Asian restuarant in Belltown.

A guy from McGill, Saurabh, was showing me his mobile-optimized graphics engine.

``It's really close to the metal.  To optimize for mobile, I had to directly
open up buffers for matrix operations.  Cool stuff.''

A waitress brought us warm saki and sashimi, and we talked about our other
interviews.  All of us had interviewed at Facebook, some of us at Google.  

I smiled at myself in the bathroom mirror after pissing.

One guy, also from Cornell, told us about his internship at Palantir.  He talked
about his boss, who was brilliant with computer science fundamentals.  They had
done acid together at work.

``That's terrifying,'' I said, thinking of Palantir's glossy black office in
Chelsea.  I then imagined Private Chelsea Manning alone in Iraq, trying to find
some sort of connection on the Internet, while trying to act ``normal'' with her
boss.

After dinner, we decided to go to a legal recreational marijuana shop, the first
and only in Oregon.

The cab driver knew exactly where we wanted to go.  I felt slightly ashamed, but
the purchasing experience was amazing.  Someone greeted us at the door, and the
people behind the display cases seemed to share our disbelief at process
of buying weed legally.

After going to another restaurant, we found a park somewhere near our hotel.

We removed the pre-rolled joints from their tubes and passed around a lighter.
By the time I finished my joint, I felt pretty high, but not paranoid or
dysphoric.  The other guys were stupidly high.

Saurabh stared at each of us with wide eyes.  ``Do any of you guys feel that you
might not die?  Like, you might live forever because of computers,'' he said.

The sober Taiwanese guy laughed nervously and manically.  I smiled and listened
to the wind above.

``Like Amazon Web Services is a living thing, sort of?  It does homeostatis.
And if we get offers from Amazon our code will become a part of it.  This sort
of process will continue until the uh recent advances in statistical machine
learning are unified with the symbolic AI research of the eighties and the
singularity happens.''

I thought about the dark silicon in the Palantir office, now.  The other Cornell
guy was rocking back and forth.

``People who don't understand computers are going to have to have a hard time,''
said the Cornell guy.

``Yeah, they're fucked,'' said Saurabh.

``I don't know,'' I said.

\plainfancybreak{12pt}{2}{* * *}

The next morning I woke up early for a jog.

I had a bit of a weed hangover, so things felt surreal.  It was warm out though.

I ran downhill, towards the ocean.

When I arrived at the harbour, I walked for a moment.  The horizon seemed close,
and glassy bubbles welled up in the green water.  I thought of the programmers
at Microsoft working in this hydrated environment. 

I took a picture and texted it to my mom, thought for a moment, and decided to
tell her about the legal marajuana shop.  She didn't respond, which I found both
funny and concerning.  I had never talked to my parents about any sort of drugs
before. 

The interview had gone very well.  Assuming I got an offer from Amazon, I'd move
here. 

\plainfancybreak{12pt}{2}{* * *}

It was bitterly cold back in Ithaca.

Before my first class, I went to the erg room for forty minutes of steady state.
I felt hopeful and clear-headed after, and showered with my teammates.

When I got back to my locker, there was an email from my Amazon recruiter.  My
heart beat rapidly and my throat constricted.  "Thanks From Amazon" was the
subject.  It was a rejection.  What the hell, I thought percussively. 

I threw my phone onto a stack of clothes and started to get dressed.  I'm
totally willing to be in denial about this, I thought.  It doesn't make sense.
Unbelievable. 

\plainfancybreak{12pt}{2}{* * *}

In human-robotics interaction, the professor told us to find a partner, and then
gave us five minutes to build a tower out of spaghetti, string, marshmellows,
and tape.  It was a competition.

My partner was one of the few non-Asian women in the class.  She had a blemished
face even though she seemed to be almost thirty.  We instantly began to have
difficulties planning of our tower.  

I wanted to incorporate the string, but she didn't think it'd help.  At some
point we just started to build, and ended up with a tower that was probably the
second tallest in the classroom, until it broke at the last second.

We joked about our tower uneasily, but it was obvious that we were secretly
blaming each other, and took these things seriously.

The professor told us groups of kindergarteners typically built the tallest
towers, besides groups of engineers. 

\plainfancybreak{12pt}{2}{* * *}

The first book I read for Samuel's class was 'Dangling Man' by Saul Bellow.  I
checked it out of the library on a Saturday night during a snowstorm.

The main character was very unlikable. He did a lot of the confrontational
things I did in my bad dreams.  I dreamed of screaming at all of people in my
life, my parents, my rowing coach, my friends and teammates.  Often I quit the
rowing team, saying that I never really liked rowing anyways, and endured a
lucid, deep regret that didn't go away until my alarm went off.

After a brief period of hope I resumed the familiar Cornell cycle of hypomania,
time debt, failure, fatigue, and Internet.  At the beginning of college, I had
tried to change my habits and become the beautiful, strong, good person I wanted
to be.  But reality had forced me accept that the cycle was natural.

I still wanted some sort of catharsis.  The most important thing was rowing.

The early winter workouts were very long, but not particularly stressful or
painful.  My classes were mostly focused on group projects, and I typically had
to go to meetings after practice, and arrived home exhausted.  I was getting a
pretty consistent 6.5 hours of sleep.

My most important class was my game class.  I felt I could potentially becomea
great video game programmer.  I was happy when I was appointed group leader.  On
weekend nights I cooked for myself, but would barely be able to finish the dry
food and a tallboy of Yuengling Lager before falling asleep at my desk, trying
to write C++.

``I'm going to need a lot more attention, love, and respect!'' I wrote in my
notebook. 

\plainfancybreak{12pt}{2}{* * *}

The Valentine's Day massacre was always less awful than expected, possibly due
to the feeling of piecing in the morning and running through the forests of
Ithaca in February.  It was relatively easy to find a consisent level of pain
pain in the quiet cold, a state of pain without abject suffering. 

That evening, I went to dinner with my partner from robotics.  Her name was
Allison.  We'd chosen to work together.  

Right after Allison and I sat down at the restuarant, a small group of rowers,
mostly Juniors, came in with girls.  I nodded at them, over Allison's shoulder.
I was happy that they'd chosen the same restaurant, the one restaurant I liked
in Ithaca.  I was proud of how civilized my teammates looked, much more
civilized than the other undergraduates, who usually seemed so weak and
undisciplined.

``Have you seen the brushes that they use on cows?'' said Allison.  We were
discussing a robot that would assist dishwashers, our first assignment.

``No,'' I said.

We ate.  I was happy when Allison got a third drink with me.

Allison wanted to know where I was working after graduation.

I knew that Allison currently worked at a supermarket. 

``I'm not exactly sure yet,'' I said.  ``Probably Amazon, if I'm willing to move
to the west coast.''

``Cool,'' said Allison, nodding.  ``I think that's where I'm going to move,
too.''

``You got an offer somewhere there?''

``Yeah, at Google Research.''

``Awesome,'' I said.  ``Working on what?''

\plainfancybreak{12pt}{2}{* * *}

The workouts became darker.  

I was having trouble pushing myself.  When I was 20, during a tough workout
sometimes a good EDM song would come on and I'd feel a trickle of cold
adrenaline and want to push more.  Something about the awful situation made me
embrace it, despite the urge to look for a way out.  It had been a broken
feeling, that felt something like crying, but it was fast.

Now some part of me just wanted it to be over, for someone to call it off,
cancel the race.

\plainfancybreak{12pt}{2}{* * *}

The weekend before dry season, I drove a group of people to the rowing house on
North Campus.

When I arrived, Tom introduced me to my date from Tri-Delt.  We said hi.  She
talked to me in a very engaging way.   She asked me how drunk I wanted to get,
on a scale of 1-10, and I said 8.  She said 8 was a good number, and we did
shots.  Then we sat down for dinner.

People started to arrive as we did dishes, mostly people I recognized from other
rowing parties.  

My date and I stuck together, wandering around the crowded house. It was a nice
change from how I normally felt at these parties: ignored by non-rowers, and
darkly motivated to train harder, so I'd get more respect from my teammates.

It started snowing around midnight.  We went outside, along with almost everyone
else.  It wasn't very cold.  Some sophomores from men's and women's team were
naked, running laps around the house.

I put my arm around my date, feeling validated by the beauty of the timeless
moment.   I made sure to appreciate the long, straight country road on the
opposite side of Lake Cayuga, and the suggestive condensation on the windows of
the rowing house.  I'd felt this many times.

We made out. Her saliva had a strong taste, typical of Cornell.  An injured
rower from my year invited us up to his room, where we did lines of coke
supplied by a pretty lightweight.  I had decided to not do coke any more after
breaking up with my ex, so I just gummed some.  

I was impressed by the amount of vaporized smoke in the room, and the casual,
mature hedonistic feel.  Then we went back downstairs to dance, now very fucked
up, in a sort of stunned way.  

A heavy glass beer boot shattered accross the brick floor, and an tall Asian guy
stood at the door with his fists balled up, staring down Tom, a quiet, sardonic
rower, also from my year.  

``Oh shit,'' I said quietly, as I was pushed away from the glass by Andrew, who
was yelling "woah, woah, woah".  Tom stepped around the glass and lunged towards
the Asian guy, and we followed them outside.  The snow had stopped.

``Why is he fighting here,'' I said.  ``There's no way he can win.'' 

The Asian guy took a few steps towards Tom, raising his hands.  He was
expessionless.

``You're a fucking pussy,'' said Tom, smiling. 

The Asian guy swung at Tom, the second punch hitting above Tom's eye.  Tom threw
himself on the Asian guy, trying to punch him to the ground.  A 230lb+ sophomore
came running of the house and executed a wrestling takedown, putting the Asian
guy into a headlock and screaming at him.   Now the whole house was standing on
the porch, some laughing and some concerned.

The commodore of the heavyweight team came over and helped the sophomore drag
the Asian guy away.  We helped Tom put a rag on his bleeding eyebrow and sat
with him.  

Everyone was calm.

When the house was almost empty, my date and I agreed to leave.  We walked
silently across the suspension bridge to where she lived in Collegetown.  I felt
a pressure, trying to think of something to say.

She shared a suite with some other women from Tri-Delt, who were still up.  Once
we got into her room we took off our clothes and starting kissing on the bed.
She got up and turned off the lights.

``I can't see,'' I said.  

``Yeah,'' she said.

We kept kissing, and I took off her bra.  I'd imagined hooking up with someone
from a rowing party many times.  We moved our hands downwards and I started
fingering her, listening to her breath.  Time passed.

``Pat, stop,'' she said.

``What?'' I said.

``You're not hard, Pat,'' she said.  Her hand was on my dick.  I stared down at
her eyes, glowing softly in the dark.  I started to kiss her again.

``Stop, you're not even hard,'' she said.

I stopped, still on top of her, looking down.

``Pat...'' she said.

``You're so gay, Pat,'' she said.  ``It's okay, my best friend is gay.''

``No, I'm not,'' I said, after a few moments.

``Oh my god, yes you are.  You're so gay.  You like Tom, right?''

``What?  I'm not gay,'' I said.

``Okay, bi, then?  I could tell you really like Tom.  It's okay.''

I'd shown pictures of my rowing teammates to my Internet friends occasionally.

``I don't know,'' I said.  ``No,'' I said.

I got off of her and stared up at the ceiling.  A minute later she went out into
the hall, and then came back in and told me to get dressed.  I started to feel
distantly upset.

I put on my clothes and then she walked me to the door.  She told me that she
loved me.  As the door closed I heard her saying ``oh my god'' to her suitemates
on the couch.

I stalked home blind drunk, feeling increasingly upset and cold.  Back in my
room, I realized that I'd left my watch at her place.  I wouldn't be able to ask
for it back.  I let out a noise and punched the wall. 

I hated that watch anyways, I thought, I had been pressured into spending \$500
on it by my grandfather.  I went on facebook and messaged an Internet girl while
writing into a Google doc, mostly in all-caps.  Then I put myself to sleep.

\plainfancybreak{12pt}{2}{* * *}

The next morning I woke up without a hangover, and jogged to North Campus to get
my car.  

The first essay for Samuel's class was due on Monday.  It was time to change my
life.  I wrote the first third of the essay before noon, writing about Joseph's
initial rejection of the 'code of the athlete', and the eventual failure of
self-reflection.

I went to the dining hall for lunch, and did an assignment for my scalable
systems class while reflecting on what I wanted in life.  It seemed that what I
wanted most keenly was a brand-name job at Facebook, Google, Amazon, Goldman
Sachs, J.P.  Morgan, etc, and the feeling of success that would come with it.
Getting a job like that seemed the easiest way to fix my life, even if I knew it
probably wouldn't really fix my life.  But from my parents persepctive, everyone
else's perspective, it would.  I wanted it more than I wanted the dismal,
shameful, self-delusional success that I could possibly find in writing or game
development.  I wanted it the way I had wanted to hook up with hot, normal
college students, for the same reason that Samuel wanted to state school. 

I went to get more pancakes.  My yoga class would start soon.  I felt a petulant
stab of anger at the events of the night before.  I had done everything right,
in college, after a rough start.  I couldn't figure out why Facebook and Amazon
hadn't given me an offer, and I didn't understand why I'd been so alone all
throughout college. 

\plainfancybreak{12pt}{2}{* * *}

During my first fall on the Cornell rowing team, I had a constant sense that all
of my teammates were calling me ``faggot'' or ``pussy'' behind my back.  I
imagined that if I showed my ``true self'' their friendliness would turn into
open hate, like when you killed allied soldiers in a video game, and they start
attacking you and your crosshairs on them go from green to red. 

At Monday morning lift we were testing max squat and max pullups.  After the
warmup Tom and Gordon came over, Tom grinning in a shit-eating way.  He had an
extremely swollen eye, he had told Coach it was caused to 'pond hockey', causing
laughter.

``Yo, Steadman, how was it with uh, Jennifer?  She was all over you,'' said Tom.  

``I don't fucking know, man,'' I said.

``She like, told us you were bi?  What?  I was like Steadman?  No.''

``Yeah, no.  I was just really fucked up,'' I said.  We stopped talking while
the weight room coach gave us the standard instructions for the squat test.

``Yeah, she was telling us...she said you said you were bi.  I was like
Steadman?  I don't think so.''

``I have no idea what the fuck I said.''

``Didn't seem like you really liked her that much,'' said Tom.

``Yeah, nah,'' I said.  ``Good times though.''

``Yeah buddy,'' said Tom, and we went to find spotters for the test.

I did well on both the squat test and the pull up test, putting up some of the
most weight on the team.  In the locker room people asked me how much I had
squatted and were impressed.  I felt optimistic about my chances for my final
season and went to Uris library and took a nap before my first class.

I felt good.

\plainfancybreak{12pt}{2}{* * *}

I had to stay up late to finish Samuel's essay.  A few hours before it was due I
finally went into the cave to finish the last two pages.  I ended up going to
bed at 3:30am.

This messed up the rest of the week and I got somewhat sick.  It was a prelim
week and a lot was due.

I emailed coach to tell him I had a fever and wouldn't be at practice, and then
met Allison at the robot lab to work on our teleoperation code.  We merged our
branches.  Allison's code was non-functional overall but included a bit of
linear algebra that corrected an issue I had with negative rotations
for the robot's arm.

A little bit after midnight we walked home together, both shivering hard.  I
felt lightheaded, but very happy talking to Allison.  I stopped at Collegetown
Bagels to get some protein shakes and Gatorade.  It was full of drunk people.  I
felt sexually frustrated in a tired way.

Practices on Tuesday, Wednesday, and Thursday went well.  On Thursday night, I
worked with my game team on code that created physics bodies for the level
files.  Around 4AM I went home.  When I awoke the Russian guy had written a
minimal character controller that allowed the player to move around the radial
geometry of the levels.

I felt happy, I was into the programming of the game.  At practice that evening
we did a 3x10, the workout I struggled with the most.  I drank a RockStar energy
drink beforehand and managed to get through it.  There would only be a few more. 

Things always seemed better when I was in control of my behavior.

We did bracket racing on Saturday morning.  It was sunny and warm.  On Saturday
an injured rower came over and I installed ``Deus Ex'', a video game highly
recommended by 4chan.   On Sunday I went to yoga with a friend who I still kind
of wanted to date.

My quads felt large and hammy.  In distributed systems class, the professor
talked about byzantine failure.  We were surprised by an easy workout Monday
night.  It was warm and we jogged to the Cornell plantations.

The big issue was whether or not I would live out my life dreams.

\plainfancybreak{12pt}{2}{* * *}

I turned 23, having dinner with my parents at the Hotel School restaurant.  It
was a happy experience.  I told them I was evaluating the offer from Amazon, but
was looking for other options.

I ground through March, trying to minimize the time lost to lying in bed with my
phone.  It was cold again.  The new Drake album came out, and I listened to it
walking to class.  I could always summon this hypomania, especially after
practice.  This hypomania had been the one constant of my time at Cornell.  In
the fall of 2013 this had led to a very strange form of depression, when my
life was falling apart but I felt very good but I felt very good because I was
going to practice twice a day, and showering.  Eventually I signed up for a
Gannet psychiatrist, and an anti-depressant and dropping some classes helped to
fix things.

We had our first 2k.  It went well.  I went right into the pain cave at the
right time, with about 800 meters to go.  I rowed reasonably well in the yellow
miasma and was able to sprint.  

``Wow, Steady, looks like you're going to PR this year,'' said a rower from my
year at dinner.  We were all relaxed and happy at the same time.  Girls came
over and we put music on our record player. 

\plainfancybreak{12pt}{2}{* * *}

The inlet was still choked with ice during the week before spring break.  We
carpooled the twenty minute drive up the lake, where the water was clear.  I was
happy to be boated, but the practices were long and frustrating.  Everything was
due on Friday, including a milestone for the game. 

Thursday was sunny but cold.  My housemate Max drove us up the lake after
class, because we were boated together. 

We did five minute rate-capped pieces against the 3V, starting half a length up
on them.  No one seemed very motivated in my boat: it was a weird mixture of
bright, windy, and cold, that felt like skiing weather.

Coach Terry, who annoyed me a lot, drove over in his launch to talk to us during
the downwind paddle.  When my pair was out, I stuck a hand down under my balls
to try to keep my fingers from going numb, which made it hard to control the
oar.

``You guys have to commit,'' yelled Coach Terry.  ``You ever heard the story
about the chicken and the pig?'' 

``No,'' said our coxswain.  

``Okay, a man makes his son a bacon and egg breakfast.  The father asks his kid,
what's the difference between the bacon and the eggs?  The kid is like what, I
don't know, and the father says: ``The chicken worked hard to make this
breakfast.  But the pig, he was committed.''

``What does that mean,'' I said to myself.

We did a few more pieces which went worse.  I didn't get any feeling of torque
or swing.  The water was cold and heavy, I supposed. 

It was still fully light out when Coach told us to dock.  The 3V was going to do
some more drills.  Coach Terry was talking to us while the coxswain was working
into the wind to the dock.  Terry started overriding the coxswain's orders and
we missed the dock and started being blown into the rocky beach.  I sculled the
blade of the person in front of me but the boat was stalled.

The coxswain muttered under her breath.  She was the hot coxswain, but no one
respected her.  Eventually we all yelled and agreed to get out of the boat and
wade it in.

My socks slipped over the algea-covered rocks, and my feet started to freeze as
we tied the boat down on the soggy grass.  I shook the seashells out of my
leather boat shoes, sitting on Cristian's bumper.  It was another absurd
practice.  

During the silent ride back to campus I warmed up.  I left my shoes outside of
my apartment, they were ruined.  I took a hot shower and then went to the
computer science undergraduate lounge to work on the game.

I got two RockStar energy drinks and a chicken parm in Duffield.

Most of the team was there.  For a while, we all worked silently.  I was
finishing up the death bounding box for the level.  Ivan and Joseph were
talking about the memory leak.

``About 300 megabytes on each level load,'' said Ivan.  ``Christ,'' I said.

Mentally I imagined 300 medium-length novels.

\plainfancybreak{12pt}{2}{* * *}

I slept deeply from one to four in the afternoon and then went to practice,
which turned out to be a relaxing 3x30 minutes of steady state.  It was warm
enough to run outside, and it was still light out.

I felt lightheaded.  That night, as I felt the incredible release of the
beginning of spring break, I knew I was sick.  

I had pneumonia.  I emailed the coaches, saying it might be a few days before I
could practice.  

I got as much food and beer as I could carry back from the 7/11.  I decided I'd
give myself a day or two to recover.  I started to drink and play Deus Ex.  

I did this for three days.  My pneumonia was pretty bad, requiring me to go to
the bathroom to cough bile into the toilet.  I felt guilty about not being at
practice, but it was okay.  I felt more guilty about not working on the game.


At the same time, I knew that experiencing Deus Ex, the game of the year in
2000, was important for me.

I played very late into the night, my space heater at my feet.  I got so drunk
that the display swam in front of me, and I felt that the old graphics were
impossibly beautiful.  When I drank wine or beer in Deus Ex, the screen got more
and more distorted with every drink.  Sometimes it was almost impossible to tell
what I was doing, in the dark underground areas of the game, or stumbling around
my basement apartment, coughing in the bathroom.

It was one of the happiest times I had during college.

\plainfancybreak{12pt}{2}{* * *}

After my sickness, rowing felt like a big nuisance.  I rejoined the team halfway
through break, jogging on the shore to get my lungs back.  I ran into the iced
over glens, and took a selfie in front of the largest waterfall.  

I was still boated for the first race of the season, at Harvard.  My boat
practiced in the morning, when it was dead calm.  The bow of the broke up a thin
film of ice on the surface of the water, which catalyzed a pinging reaction all
across the lake.  Sometimes I would fall asleep in class, or quiet early during
an extra workout.  I didn't let these moments derail me for any significant
length of time: I knew that even if I quit, I could potentially un-quit.  I
could always depend on listening to loud EDM as I walked between classes to make
me feel a dark euphoria, that I could tap into on the rowing machine.

It was my first time at the Harvard boat house.  The long bus ride to Cambridge
and the meals at the hotel gave me time to think over my life.  Was I a scrub?
Inevitably I thought of Mark Zuckerberg and the men who had rowed in this
boathouse, beautiful people. 

After a brutal last three hundred meters, we won our race in the basin.  As my
stroke started to fall apart near the end of the race I looked over my shoulder
for the finish, the first time I'd ever done so in a race.

\plainfancybreak{12pt}{2}{* * *}

Well, here I am ... 23 and still rowing.  I'm not much better at rowing.  I'm
somewhat better at school.  I've had one relationship.

Navy/Syracuse

Allison?


\plainfancybreak{12pt}{2}{* * *}

The next day I sat down with a Coors Light and Life cereal to watch the video of
the Navy-Syracuse race.  I was buzzed and excited to relive the race. 

My excitement quickly turned to horror.  The video feed still had audio, and
right after the start one could hear Coach Terry say ``We've got to get Steady
out of there, I talked to him and he didn't make a change.''  It was obvious
what he was referring to: I was leaning away from my oar at the end of every
stroke, through the whole race.

It fucked me up.  I knew the coming week was going to be painful and
humiliating: they would seat race me out of the boat.

I made myself immediately head out the door to yoga class.  

The thought of not racing again was very painful.  I had always imagined
preparing for my last race: ideally in June, after graduation.

I had imagined waking up one morning in early June, and looking at my body in
the mirror, knowing it was the best it would ever be.  Then I imagined  the
finish of the race, falling back into the fragile boat, my hands slapping the
cool water and my eyes closing, and it being over.

But now it seemed like I wouldn't get that moment.  Or, it had already happened.


It was painful to be a loser in their presence.  

Things that make me happy: exercise, video games, reading, flirting, interneet
messaging, programming, drawing, money , free time, writing

I'm just so disgusted by my presence in the world.

``All of my friends that I admire seem to hate themselves pretty regularly,''
said Samuel placidly.  ``It's something I've come to accept.''

``I don't want to hate myself, it's fucking stupid and I'm sick of it,'' I said.  

Samuel didn't respond.

``Maybe I should just accept the Amazon offer and move to Seattle,'' I said.
``It'll be okay.''

``No, you should move to New York and be glamorous,'' said Samuel.  ``I think
when you look back on rowing it will be very indistinct for you.'' 

Maybe I should have quit two years ago.  I had never seriously considered the
idea before.

I had often imagined the end of rowing.  Surprisingly, there was no seat racing on Monday morning, and I kept my seat in
the boat.  But on Tuesday...

During early spring I was usally awoken a few minutes before my 5:50 AM alarm by
the sound of my teammates coming down the stairs and getting some breakfast.  I
had developed the habit of waking up around 4:30 AM to drink a Gatorade and eat
a peanut butter and jelly so I'd wake up hydrated and ready to pee, so there
wouldn't be any pressure on my bladder in the boat. 

``You're living life,''

I looked up at the hills above campus, knowing it might be the last time I rowed
in a serious way on Lake Cayuga.  Won by about a length of open water.  ``Yeah
'' 

I knew that despite the part of me that wanted to be like these warlike youth,
my equilibrium was being quietly manic on my computer, in the the place I'd
found myself in during spring break.  I cared more for the virtual text of any
given momment than I cared about winning or losing.  I had never really wanted
to exert myself like this, but of course I had been necessary to try.  I'd done
it to prove something to myself and others, and to some degree I'd be
successful, but now it was over and I still felt alone and unsuccessful.

I put on my rowing trou and a tank top, but on the way to the erg room the
heaviness in my throat won and I went to the bathroom.  A few lightweight
rowers were still there putting on sunscreen, so I went into one of the stalls.
Then I willed myself to start to crying heavily but silently, in a fully warm
and cathartic way.  

It was more bitter than I had hoped.  It was like many springs in middle school
and high school, 

It was like being kicked in the face every day.

\plainfancybreak{12pt}{2}{* * *}

``Come back to Donlon with us, we have some presents for you,'' said my mom. 

``Okay,'' I said.  

We made the long walk back to the dorms.  My grandfather said something about
how he remembered work seeming like a vacation after college, and that I could
start making real money now.

``I'm not so sure I'll be focusing on that, right after graduation,'' I said,
and immediately regretted it, thinking about him at my age, with a four year old
daughter.  He was silent.  My dad and I talked about my plans for the next
couple months.  I again had the feeling that my grandfather despised me, even if
he didn't know it himself.  I pushed the thought to the side, thoughts like that
weren't any good for a 23 year old.

Back at the dorm I sat around while my sisters changed.  I felt relaxed.

I opened presents from my aunt and great aunt first.  Both had given me \$100
checks.  I was surprised and happy.  My parents had given me new shoes, and
would later send me an e-card for \$1000, saying they were proud of my hard
work.  

Finally I opened the present from my grandparents.  The card on the outside
contained a check for \$4000.  

``Thank you so much,'' I said.
